% !TEX root = rapport.tex

\begin{abstract}
This paper reviews the history, current state, and future of input and output methods, and the factors leading up to their invention. The paper hopes to explain what the current trends in development are and what new applications they may allow.

The paper summarises the history of a selected set of computer interaction devices, from punch cards to the mouse and keyboard, and goes on to investigate the devices in popular use today. Using the knowledge about the factors that lead up to the creation of previous and contemporary devices, the paper goes on to present two possible future methods that follow the same trend of development; gesture control and brain-computer interfaces. A number of solutions are covered, aimed towards those with need of assistive devices.

The report concludes that the interaction method development has become highly user-centered, and goes towards a higher level of abstraction between the user and the machine. It also shows that advances in technology not necessarily replace the previous technology, but rather broaden the spectra of applications where computers are used.

Input and output devices and methods is a broad subject and this paper does not assume to present a complete coverage thereof. It rather presents a deep enough coverage of its most prominent aspects in the field, in order to see the general patterns.



Denna artikel granskar historiska, nuvarande och framtida användargränssnitt för datorer, och de faktorer som driver deras utveckling. Artikeln avser att förklara vilka de nuvarande utvecklingstendenserna är, och vilka nya tillämpningar dessa medger \todo{medger?}.

Artikeln sammanfattar en utvald uppsättning användargränssnitt, från hålkort till mus och tangentbord, samt undersöker de gränssnitt som är i populärt bruk idag. Genom att använda kunskapen om tidigare och samtida enheters utveckling presenteras två möjliga framtida gränssnitt som följer samma utvecklingstrend; gesture control och brain-computer gränssnitt \todo{svengelska}. Artikeln behandlar även ett antal lösningar för personer med handikapp, i behov av särskillda hjälpmedel.

I artikeln dras slutsatsen att utvecklingen av användargränssnitt i allt högre grad blivit användarcentrerad, och eftersträvar en högre abstraktionsnivå mellan dator och människa. Den visar också att de nya gränssnitten inte nödvändigtvis ersätter de tidigare, utan att de snarare kompletterar varandra och breddar uppsättningen användargränssnitt som används.

Användargränssnitt för datorer är ett brett ämne och denna artikel avser inte presentera en fullständig redogörelse av dessa. Den avser snarare presentera en tillräckligt bred täckning av dess mest framträdande aspekter, i syfte att se generella mönster.

\end{abstract}
