% !TEX root = rapport.tex

\section{Introduction}

The history of computing is arguably short, but has already seen many advances. Its history is interwined with that of the input and output methods it uses; changes in the way we use computers have altered the way we choose to interact with them, and changes in the way we interact with computers have in turn changed the way we use them.

Today the classical way to use a computer is with a computer terminal, using a mouse and keyboard. Although this is a working configuration on a desktop, it does not cope with the demands of the mobile devices currently growing in popularity. Touchscreen technology used in mobile devices have not lead to mobile devices taking the place of the traditional computer. Instead, it has broadened the spectra of applications for computers, bringing them into our everyday life. This inspires us to investigate the history leading up to todays dramatic changes in computer usage, in the hopes of better understanding the challenges of today and get a glimpse of the interaction methods of tomorrow. Understandably, a large variety of devices have been developed over time and cannot be exhaustively covered in this paper.

This inspires us to investigate the history leading up to todays dramatic changes in computer usage, in the hopes of better understanding the challenges of today and get a glimpse of the interaction methods of tomorrow.

The roadmap of the paper is as follows. To start off with, we investigate the history of the terminal interface in chapter \ref{history}. In chapter \ref{current} we summarize the history of contemporary input methods and analyse their effect on our relationship toward computers. In chapter \ref{future}, we explain some of the technologies currently in development and attempt to predict the impact they could have on our future use of computer technology.

The devices covered here in the historic section are those devices which, according to the authors, have had a big impact on the development leading towards the computer keyboard and mouse. In the section on contemporary input methods, touchscreens are covered due to their recent popularisation, as well as speech recognition as it is a field which have seen great advances lately. The possible future input methods covered in this article are gesture control and thought control, as these methods have the potential to greatly reduce the friction in human-computer interaction compared to contemporary methods.

\todo{How do we smoothely cover special-purpose, and what do we actually say in that section?}

The roadmap of the paper is as follows. To start off with, we investigate the history of the terminal interface in chapter \ref{history}. In chapter \ref{current} we summarize the history of contemporary input methods and analyse their effect on our relationship toward computers. In chapter \ref{future}, we explain some of the technologies currently in development and attempt to predict the impact they could have on our future use of computer technology.
